Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-06 eswc-2012/phdsymp.tex
hypothesis testing vs evidence
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@155 43ef1190-90fd-4dd7-a769-d0121f02b80e

The focus on SPARQL benchmarking is not only motivated from the
perspective of optimization, as I have found the current state of the art
in SPARQL benchmarking lacking in its use of statistics. The emphasis
in the present paper is on statistics in benchmarking with the purpose
of putting it on a firmer foundation from a hypothesis testing
perspective.

>>>>

The focus on SPARQL benchmarking is not only motivated from the
perspective of optimization, as I have found the current state of the art
in SPARQL benchmarking lacking in its use of statistics. The emphasis
in the present paper is on statistics in benchmarking with the purpose
of providing a firmer foundation on which assertions about engine
performance can be backed with evidence.
